---
title: "CaseStudyTwo"
author: "Jim Park Asha Saxena Andrew Walch"
date: "November 25, 2017"
output: 
   html_document:
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#2a Read the csv into R and take a look at the data set. Output how many rows and columns the data.frame is.

```{r}
PD <- read.csv("Procrastination.csv")
dim(PD) #results in printing the number of rows then the number of columns.
```


#2b The column names are either too much or not enough. Change the column names so that they do not have spaces, underscores, slashes, and the like. All column names should be under 12 characters. Make sure you’re updating your codebook with information on the tidied data set as well.

```{r}
class(PD)
OldNames <- names(PD)
library(data.table)
PD.renamed <- setnames(PD, old=OldNames, new=c("Age", "Gender", "Kids", "Education","WorkStatus","AnnualIncome", "Occupation", "Years", "Months", "Community", "Country", "Status", "NumSon", "NumDaught", "DP1", "DP2","DP3","DP4","DP5","AIP1","AIP2","AIP3","AIP4","AIP5","AIP6","AIP7","AIP8","AIP9","AIP10","AIP11","AIP12","AIP13","AIP14","AIP15", "GP1", "GP2", "GP3", "GP4", "GP5", "GP6", "GP7", "GP8", "GP9", "GP10", "GP11", "GP12", "GP13", "GP14", "GP15", "GP16", "GP17", "GP18", "GP19", "GP20", "SWLS1", "SWLS2", "SWLS3", "SWLS4", "SWLS5","Q1Self","Q2Others"))
head(PD.renamed)
```

#2c. Some columns are, due to Qualtrics, malfunctioning. Prime examples are the following columns: “How long have you held this position?: Years”, Country of residence, Number of sons, and Current Occupation.

i Some have impossible data values. Detail what you are doing to fix these columns in the raw data and why. It’s a judgment call for each, but explain why. For example, most people have not been doing anything for over 100 years. For the “Years” columns, round to the nearest integer.

ii Somehow, “Number of sons” was labeled with Male (1) and Female (2). Change these incorrect labels back to integers.

iii There are no “0” country of residences. Treat this as missing.

iv Current Occupation has no “please specify” or “0.” Treat them as missing. Some jobs are quite similar. Use judgment calls to make overwrite them into the same category. It does not have to be 100% accurate, but right now “ESL Teacher” would not be counted as “teacher” if there were unique counts.

#2Ci. Fix impossible data values.  Round Age and Years to nearest integer (negative exponents will default to 0 due to this), Correct Years '999' entries and treat as missing(NA), and correct number of sons entries where Male = 1 sons, and Female =2 sons, Change 0 in "Country" to NA to indicate the data is missing, change "please specify" or "0" under Occupation to NA to indicate missing, and combine similar occupations into category of occupation.
```{r}
PD.renamed$Age <- as.integer(round(PD.renamed$Age)) #rounds all Ages to the nearest integer and converts from numeric to integer.
PD.renamed$Years <- as.integer(round(PD.renamed$Years)) #rounds all Years to the nearest integer and converts from from numeric to integer.
PD.renamed$Years <- as.integer(gsub(999, NA, PD.renamed$Years)) #Removes 999 values and treats them as missing by indicating with an NA
PD.renamed$NumSon <- (gsub("Male", 1, PD.renamed$NumSon)) #subs a 1 where the word Male is listed in NumSon
PD.renamed$NumSon <- (gsub("Female", 2, PD.renamed$NumSon)) #subs a 2 where the word Female is listed in NumSon
PD.renamed$NumSon <- as.integer(PD.renamed$NumSon) #Converts NumSon to an integer.
PD.renamed$Country <- gsub(0, NA, PD.renamed$Country) #displays Country with 0 as missing data (NA)
PD.renamed$Country[PD.renamed$Country == ""] <- NA #replaces all non-entries with NA
PD.renamed$Occupation[PD.renamed$Occupation == 0] <- NA
PD.renamed$Occupation[PD.renamed$Occupation == "please specify"] <- NA
PD.renamed$Occupation[PD.renamed$Occupation == ""] <- NA
```
#2e.  Each variable that starts with either DP, AIP, GP, or SWLS is an individual item on a scale. For example, DP 1 through DP 5 are five different questions on the Decision Procrastination Scale. I’ve reverse-scored them for you already, but you should create a new column for each of them with their mean. To clarify, you’ll need a DPMean column, an AIPMean column, a GPMean column, and a SWLSMean column. This represents the individual’s average decisional procrastination (DP), procrastination behavior (AIP), generalized procrastination (GP), and life satisfaction (SWLS).


```{r}
PD.renamed$DPMean=rowMeans(PD.renamed[,15:19]) #Creates column for mean of all DP entries in observation.
PD.renamed$AIPMean=rowMeans(PD.renamed[,20:34]) #Creates column for mean of all AIP entries in observation.
PD.renamed$GPMean=rowMeans(PD.renamed[,35:54]) #Creates column for mean of all GP entries in observation.
PD.renamed$SWLSMean=rowMeans(PD.renamed[,55:59]) #Creates column for mean of all SWLS entries in observation.
PD.renamed[,62:65] <- round(PD.renamed[,62:65], digits = 1) #Round DP, AIP, GP, and SWLS means to 1 digit.
head(PD.renamed[,62:65])
```

##3 SCRAPING
#3a Scraped Country and HDI
```{r, echo = TRUE}
library('rvest') # grab and parse HTML

#Specifying the url for desired website to be scrapped
url <- 'https://en.wikipedia.org/wiki/List_of_countries_by_Human_Development_Index#Complete_list_of_countries'

webpage <- read_html(url)#Reading the HTML code from the website

#Using XPath selectors to scrap the Country and HDI of first 8 tables
Country<-webpage%>%html_nodes("h3+ div .wikitable:nth-child(1) td:nth-child(3)")%>%html_text()
HDI<-webpage%>%html_nodes("h3+ div td:nth-child(4)")%>%html_text()

###  WILL NEED TO FIX "WORLD" ENTRY
CountryHDI <- data.frame(Country, HDI)#Convert to data frame
CountryHDI

## TODO need to fix "world" entry
```

